### 2019-05-11 paper/paper.tex
Done

\newpage
\section{Introduction}
The software industry is transforming at a rapid pace to accommodate the dynamic nature of the market and as a result, it continues to struggle to find process-identity with continuous software engineering.

The software engineering community has for a few decades experimented with the concept of distributing software in faster release cycles; endeavoring to do so without sacrificing reliability and security. To achieve such a goal, there has been a widespread movement in the technical community to advocate for using Agile practices, and in particular: continuous integration, delivery, and deployment. The traditional methods of software development no longer meet the need of businesses that -- now more than ever -- want to proactively engage and retain their customers. The organizational transition to Agile practices demands a large mentality change and require individuals to recognize software as incremental features developed with cross-collaboration of small comprehensive team units, as opposed to large modules developed by siloed units.

@@

Of the ideal software practices that are commonly known and trending vocabulary -- continuous integration, delivery, and deployment -- come with the responsibility of defining them. Many software professionals, however, have misunderstood these development practices and at times, infuse them as one concept without careful and thoughtful distinction. It would, therefore, be wise to define each component for what they represent and why it matters.

@@

An added layer of complexity that makes defining what it means to do continuous software engineering more difficult is the well-documented phenomena of non-collaboration between software developers and academic researchers. Computer scientist and software engineering professor, Jan Bosch, states that even the greatest developers in the software industry view top academic researchers as people who give insignificant learning value and the converse being true as well \cite[p. ~29]{bosch_2014}. In particular, top researchers do not believe that top developers contribute much to their body of research. The intrinsic difference between the developer and researcher is in how they view the values of software engineering as a means to a different end. Developers by nature of their work are expected to produce software in a timely business-oriented manner, wherein researchers are focused on the insights that data analysis can accomplish.

@@

A particular issue that plagues the software industry is the traceability of requirements in the context of using continuous practices.

On the topic of continuous integration alone, Daniel Stahl points out the problems that the software industry is facing \cite[p. ~60]{stahl_2017}:

The software engineering community is still in the early stages of understanding and implementing continuous practices. It will take time for the community to find engineering standards for continuous practices to mitigate the risks while taking advantage of its' benefits.

    \subsection{Struggles of Traceability}
        \subsubsection{Importance}
        \begin{itemize}[noitemsep]
            \item What is the importance of traceability for the software engineering community?
            \begin{itemize}
                \item \cite{stahl_2017} \& \cite{stahl_hallen_bosch_2016}
            \end{itemize}
        \end{itemize}
        \subsubsection{Problem of Mapping}
        \begin{itemize}[noitemsep]
            \item What is the problem of mapping requirements to implemented code and the converse?
            \begin{itemize}
                \item \cite{stahl_2017} \& \cite{stahl_hallen_bosch_2016}
            \end{itemize}
        \end{itemize}
        \subsubsection{Eiffel Framework}
        \begin{itemize}[noitemsep]
            \item What is the proposed solution to address traceability issues in CI/CDE/CD environments?
            \begin{itemize}
                \item \cite{stahl_2017} \& \cite{stahl_hallen_bosch_2016}
            \end{itemize}
        \end{itemize}

\section{Conclusion}

>>>>

\newpage
\section{Introduction}
The software industry is transforming at a rapid pace to accommodate the dynamic nature of the market and as a result, it continues to struggle to find process-identity with continuous software engineering. The software engineering community has for a few decades experimented with the concept of distributing software in faster release cycles; endeavoring to do so without sacrificing reliability and security. To achieve such a goal, there has been a widespread movement in the technical community to advocate for using Agile practices, and in particular: continuous integration, delivery, and deployment. The traditional methods of software development no longer meet the need of businesses that -- now more than ever -- want to proactively engage and retain their customers. The organizational transition to Agile practices demands a large mentality change and require individuals to recognize software as incremental features developed with cross-functional collaboration of small comprehensive team units, as opposed to large modules developed by siloed units.

@@

Of the ideal software practices that are commonly known and trending vocabulary -- continuous integration, delivery, and deployment -- come with the responsibility of defining them. Many software professionals, however, have misunderstood these development practices and at times, infuse them as non-differing concepts without careful and thoughtful distinction. It would, therefore, be wise to define each component for what they represent and why it matters.

@@

An added layer of complexity that makes further refinement of what it means to do continuous software engineering more difficult is the well-documented phenomena of non-collaboration between software developers and academic researchers. Computer scientist and software engineering professor, Jan Bosch, states that even the greatest developers in the software industry view top academic researchers as people who give insignificant learning value and the converse being true as well \cite[p. ~29]{bosch_2014}. In particular, top researchers do not believe that top developers contribute much to their body of research. The intrinsic difference between the developer and researcher is in how they view the values of software engineering as a means to a different end. Developers by nature of their work are expected to produce software in a timely business-oriented manner, wherein researchers are focused on the insights that data analysis can accomplish. There has been little progress between the two groups but some effort has been made by the Software Center to create mutually beneficial and collaborative work on software engineering issues \cite[p. ~31]{bosch_2014}.

Alone on the topic of continuous integration, Daniel Stahl plainly points out the problems that the software industry is currently facing \cite[p. ~60]{stahl_2017}:

Continuous integration aims to solve these types of scaling issues but is a significant challenge to implement in its own right. There are many cases where organizations have successfully implemented continuous integration in a large-scale context despite the complexity. Stahl's findings from his case studies supports that a key enabler for success in implementing continuous integration is the communication of a shared vision within an organization, but should be further examined for legitimacy \cite[p. ~86]{stahl_2017}. Bosch would argue that in an Agile environment, which continuous practices rightfully belongs, leadership culture needs to change to a more suitable style of support, rather than the old command and control style \cite[p. ~209]{bosch_2014}.

@@

\section{Conclusion}
The software engineering community is still in the early stages of understanding and implementing continuous practices. It will take time for the community to find engineering standards for continuous practices to mitigate the risks associated with it while taking advantage of its' benefits. It is important to further refine these engineering solutions as the software industry slowly transition to and embrace the Agile culture. It could very well be that in the near future -- in order to survive as an organization producing and selling software -- that Agile and its subset, continuous practices, become a necessity rather than just a different way of development. The consumers will be the decisive factor as more and more of them expect quality software products at a faster pace.
